%-------------------------
% Resume in LaTeX
% Author: Ishaan Goel
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{3.60004pt}

% Adjust indent size
\newcommand\indentsize{10pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \item\vspace{-2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \normalsize
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label=]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=\indentsize, label=-]\vspace{-7pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \Huge Ishaan Goel \\ \vspace{2pt}
    \large
    \href{tel:17712017576}{+1 771-201-7576}
    $|$ \href{mailto:igoeldxb@gmail.com}{igoeldxb@gmail.com}
    $|$ \href{https://linkedin.com/in/igoeldc/}{linkedin.com/in/igoeldc}
    $|$ \href{https://github.com/igoeldc}{github.com/igoeldc}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeSubHeadingListStart
    \item{AI Researcher and developer with deep quantitative foundations, demonstrated success in architecting a multi-agent RAG system for a 1,000+ user enterprise. Seeking to apply expertise in generative AI and stochastic modeling to solve complex problems in NLP and computational finance.}
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EDUCATION-----------
\newcommand{\resumeEducationHeading}[9]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2} & #3 \\
      \hspace{\indentsize} #4 & #5 \\
      \hspace{20pt} #6 & \\
      \hspace{20pt} \textit{#7} & \\
      \hspace{\indentsize} #8 & #9
    \end{tabular*}
}

\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {\href{https://www.iit.edu/}{Illinois Institute of Technology}}{(3.73/4.00)}{Chicago, IL}{Dual B.S. \href{https://catalog.iit.edu/undergraduate/colleges/computing/applied-mathematics/bs/\#text}{Applied Mathematics} and \href{https://catalog.iit.edu/undergraduate/colleges/computing/computer-science/\#:~:text=The\%20B.S.\%20in\%20Data,be\%20successful\%20data\%20science\%20professionals.}{Data Science}}{Aug 2022 -- Present}{Minor in \href{https://catalog.iit.edu/undergraduate/colleges/business/minor-finance/\#:~:text=business\%20schools\%20worldwide.-,Required\%20Courses,-Course\%20List}{Finance}}
      {Recipient of the Heald and STEM+ Scholarships}{M.A.S. \href{https://catalog.iit.edu/graduate/colleges/computing/computer-science/master-artificial-intelligence/\#overviewtext}{Artificial Intelligence}}{Aug 2024 -- Present}
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
\resumeSubHeadingListStart
    \item \textbf{Math:} Probability, Linear Optimization, Intro to Stochastic Processes, Graph Theory, Monte Carlo Methods in Finance \vspace{-5pt}
    \item \textbf{AI/ML:} Machine Learning, AI Language Understanding, Data Mining, Data Preparation and Analysis \vspace{-5pt}
    % \item \textbf{Other:} Language Theory in NLP, Deep Technology Commercialization \vspace{-5pt}
    \item \textbf{Enrolled:} Information Retrieval, Deep Learning
\resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Research Assistant}{May 2025 -- Present}{\href{https://www.iit.edu/computing}{Illinois Institute of Technology, College of Computing}}{Chicago, IL}
        \resumeItemListStart
            \resumeItem{Developing a Markov Chain sampler in Python to generate uniformly random hypergraphs with prespecified $k$-core sequences.}
        \resumeItemListEnd

    \resumeSubheading{Research Assistant}{Aug 2024 -- Present}{\href{https://www.iit.edu/applied-math}{Illinois Institute of Technology, Department of Applied Mathematics}}{Chicago, IL}
    \textit{Under \href{https://cialenco.com}{Dr. Igor Cialenco}, \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=2407549&HistoricalAwards=false}{NSF-funded research}}
        \resumeItemListStart
            \resumeItem{Developing a stochastic mathematical framework for sustainable groundwater management under California's SGMA.}
            \resumeItem{Applying concepts from stochastic games and Nash equilibria to model groundwater rights pricing and assess policy impacts for global water markets.}
            \resumeItem{Designing computational algorithms for multi-stakeholder equilibrium analysis by integrating mathematical theory with hydrological and economic data.}
        \resumeItemListEnd

    \resumeSubheading{Intern}{July 2024}{\href{https://www.peoplestrong.com/about-us/}{PeopleStrong Technologies Ltd.}}{Gurugram, India}
        \resumeItemListStart
            \resumeItem{Developed and architected a chatbot for employee query management using Retrieval Augmented Generation (RAG) and LLMs, intended to serve over 1,000 employees.}
            \resumeItem{Designed an agentic architecture integrating 5+ specialized RAG systems, and performed A/B testing to validate the approach, leading to a planned company-wide deployment after presenting findings to leadership.}
        \resumeItemListEnd

    % \resumeSubheading{Research Assistant}{Jan 2024 -- Jun 2024}{\href{https://www.iit.edu/computing}{Illinois Institute of Technology, College of Computing}}{Chicago, IL}
    %     \resumeItemListStart
    %         \resumeItem{Modeled collective behavior in multi-agent systems with restricted fields of view by developing a simulation for a 1-dimensional Cucker-Smale model with asymmetrical communication.}
    %     \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\newcommand{\resumeProjectHeading}[2]{
    \item \normalsize
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        #1 & \small#2 \\
    \end{tabular*}%\vspace{-7pt}
}

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{\href{https://github.com/igoeldc/AI-Language-Understanding-Projects}{\textbf{Natural Language Understanding Projects}} $|$ \emph{NLP, Python}}{Aug 2024 -- Dec 2024}
        \resumeItemListStart
            \resumeItem{Built core NLP models from scratch, including a probabilistic language model, a Naïve Bayes classifier, and a $k$NN classifier.}
        \resumeItemListEnd
    \resumeProjectHeading{\href{https://github.com/jacobhthomas/CollabGraph}{\textbf{Erd\H{o}s Co-authorship Network}} $|$ \emph{Graph Theory, Python, NetworkX}}{Feb 2023 -- May 2023}
        \resumeItemListStart
            \resumeItem{Analyzed a 500+ node co-authorship network, applying centrality measures to identify key researchers and reveal collaborative patterns.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------LEADERSHIP ROLES-----------
\section{Leadership Roles}
\resumeSubHeadingListStart
    \resumeSubSubheading{\textbf{President}, Machine Learning at Illinois Institute of Technology (ML@IIT)}{Jan 2023 -- Present}
    \resumeItem{Organized speaker events and workshops on cutting-edge AI techniques, increasing attendance eighteen-fold and fostering campus-wide collaboration on AI projects.}
    \resumeSubSubheading{\textbf{Vice President}, Society for Industrial and Applied Mathematics (SIAM) Chapter at IIT}{Dec 2022 -- Present}
    \resumeItem{Spearheaded initiatives connecting students to research opportunities in applied mathematics by hosting professor talks and organizing networking events for students across multiple disciplines related to mathematics.}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Programming:} Python, R, C++, Julia, Java, \LaTeX, HTML, CSS, SQL, Mathematica, MATLAB
    \item \vspace{-5pt} \textbf{Python Stack:} PyTorch, scikit-learn, NumPy, pandas, matplotlib, Streamlit
    \item \vspace{-5pt} \textbf{R Stack:} tidyverse, caret, rpart, glmnet, e1071, keras
    % \item \vspace{-5pt} \textbf{Spoken Languages:} English, Hindi-Urdu, Mandarin Chinese, Spanish, Modern Standard Arabic, Panjabi
\end{itemize}

\end{document}